Supplementary Material for ``Provisional Title''

### 2021-04-16 draft/supp.tex
typos

\begin{equation}
d_T = \mathrm{Q}4 \left( \left\{d\right\} \right) + 
\mathrm{IQR} \left( \left\{d\right\} \right)
\label{supp-eqn:threshold}
\end{equation}
%
Where Q4 and IQR represent the fourth quantile and the interquartile range
respectively. Note that this threshold is analogous to the one used in
standard boxplots to identify outliers.

@@

\subsubsection{Special cases}\label{supp-methods:data-proc:special}

>>>>

\begin{equation}
d_T = \mathrm{Q}3 \left( \left\{d\right\} \right) + 
1.5 \; \mathrm{IQR} \left( \left\{d\right\} \right)
\label{supp-eqn:threshold}
\end{equation}
%
Where Q3 and IQR represent the third quartile and the interquartile range
respectively. Note that this threshold is analogous to the one used in
standard boxplots to identify outliers.

@@

\subsubsection{Characterizing dominant species}\label{supp-methods:data-proc:doms}

As described in the main text Methods \mr, communities were plated and the most
abundant species (as determined by counting of colony morphotypes) was isolated
and allowed to regrow in monoculture prior to sequencing. We then characterize
the isolated species to, first, make sure that they were dominant in the communities
they were isolated from, and second, identify those instances where two or more
communities share the same dominant.

Since we assembled 16 communities, we have 16 isolates. We will denote as
